---
title: "Yelp Reviewer Social Network Analysis"
author: "Apoorva Havanur, ahavanur"
date: "1/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
library(scatterplot3d)
```

This project attempts to learn more about the behavior of yelp reviews and how it becomes influenced by their social network. 

```{r}
influence.data = read.csv("outputs/influence/influence_pittsburgh.csv")
elite_users = read.csv("pittsburgh_elites.csv")
business_categories = read.csv("business_categories_pittsburgh.csv")
```
The two primary measures we are looking at in this section are influenced and influencer scores. \newline 
'Influenced' scores is the percentage of a user's reviews of a business that came *after* one of their friends on yelp reviewed the same business, i.e they went to that business due to a friend's influence.  
\newline 
'Influencer' scores is the percentage of a user's reviews of a business that came *before* one of their friends on yelp reviewed the same business, i.e they influenced one of their friends to go. 

Influence Score Histograms and EDA
```{r}
hist(influence.data$influenced_score, main = "Influenced Score")
hist(influence.data$influencer_score, main = "Influencer Score")
```

```{r}
summary(influence.data$influenced_score)
summary(influence.data$influencer_score)
summary(influence.data$total_friends)
summary(influence.data$total_reviews)
```

```{r}
plot(influence.data$influenced_score, influence.data$influencer_score, main = "Influenced vs. Influencer Scores", xlab = "Influenced Score", ylab = "Influencer Score")
plot(influence.data$total_friends, influence.data$total_reviews, main = "Friends vs. Reviews", xlab = "User's Number of Friends", ylab = "User's Number of Reviews")
```

Removing Outliers
We take out the folks with the highest friends and largest number of reviews
```{r}
p99friends = influence.data[which(influence.data$total_friends <= quantile(influence.data$total_friends, seq(0,1,0.01))[100]),]
p99reviews = influence.data[which(influence.data$total_reviews <= quantile(influence.data$total_reviews, seq(0,1,0.01))[100]),]
```

Aggregating Data by Friends and Reviews
```{r}
score_by_friends = sqldf("SELECT total_friends, AVG(influenced_score) as influenced_score, AVG(influencer_score) as influencer_score, COUNT(1) as num FROM p99friends GROUP BY 1")
score_by_reviews = sqldf("SELECT total_reviews, AVG(influenced_score) as influenced_score, AVG(influencer_score) as influencer_score, COUNT(1) as num FROM p99reviews GROUP BY 1")
```

```{r}
lin.reg.friends.influenced = lm(score_by_friends$influenced_score ~ score_by_friends$total_friends)
plot(score_by_friends$total_friends, score_by_friends$influenced_score, main = "Influenced Score by Number of Friends", xlab = "Friends", ylab = "Influenced Score", pch = 20)
abline(lin.reg.friends.influenced, col = "red")
summary(lin.reg.friends.influenced)
```

```{r}
lin.reg.friends.influencer = lm(score_by_friends$influencer_score ~ score_by_friends$total_friends)
plot(score_by_friends$total_friends, score_by_friends$influencer_score, main = "Influencer Score by Number of Friends", xlab = "Friends", ylab = "Influencer Score", pch = 20)
abline(lin.reg.friends.influencer, col = "red")
summary(lin.reg.friends.influencer)
```

```{r}
s3d = scatterplot3d(score_by_friends$total_friends, score_by_friends$influenced_score, score_by_friends$influencer_score,
              main = "Influenced vs Influencer Score Across Friend Count", xlab = "Number of Friends", ylab = "Influenced Score", zlab = "Influencer Score", type = "h", pch = 20, angle = 40)
```


```{r}
lin.reg.reviews.influenced = lm(score_by_reviews$influenced_score ~ score_by_reviews$total_reviews)
plot(score_by_reviews$total_reviews, score_by_reviews$influenced_score, main = "Influenced Score by Number of Reviews", xlab = "Reviews", ylab = "Influenced Score", pch = 20)
abline(lin.reg.reviews.influenced, col = "red")
summary(lin.reg.reviews.influenced)
```

```{r}
lin.reg.reviews.influencer = lm(score_by_reviews$influencer_score ~ score_by_reviews$total_reviews)
plot(score_by_reviews$total_reviews, score_by_reviews$influencer_score, main = "Influencer Score by Number of Reviews", xlab = "Reviews", ylab = "Influencer Score", pch = 20)
abline(lin.reg.reviews.influencer, col = "red")
summary(lin.reg.reviews.influencer)
```

```{r}
s3dr = scatterplot3d(score_by_reviews$total_reviews, score_by_reviews$influenced_score, score_by_reviews$influencer_score,
              main = "Influenced vs Influencer Score Across Review Count", xlab = "Number of Reviews", ylab = "Influenced Score", zlab = "Influencer Score", type = "h", pch = 20)
```




Creating Cumulative Distributions 
```{r}
score_by_friends$cummulative_influenced = cumsum(score_by_friends$influenced_score*score_by_friends$num)/cumsum(score_by_friends$num)
score_by_friends$cummulative_influencer = cumsum(score_by_friends$influencer_score*score_by_friends$num)/cumsum(score_by_friends$num)

score_by_reviews$cummulative_influenced = cumsum(score_by_reviews$influenced_score*score_by_reviews$num)/cumsum(score_by_reviews$num)
score_by_reviews$cummulative_influencer = cumsum(score_by_reviews$influencer_score*score_by_reviews$num)/cumsum(score_by_reviews$num)
```

```{r}
plot(score_by_friends$total_friends, score_by_friends$cummulative_influenced, main="Cumulative Influenced Score Over Number of Friends", xlab = "Cumulative Friend Count",ylab = "Average Influenced Score", pch = 20)
plot(score_by_friends$total_friends, score_by_friends$cummulative_influencer, main="Cumulative Influencer Score Over Number of Friends", xlab = "Cumulative Friend Count",ylab = "Average Influencer Score", pch = 20)
plot(score_by_reviews$total_reviews, score_by_reviews$cummulative_influenced, main="Cumulative Influenced Score Over Number of Reviews", xlab = "Cumulative Review Count",ylab = "Average Influenced Score", pch = 20)
plot(score_by_reviews$total_reviews, score_by_reviews$cummulative_influencer, main="Cumulative Influencer Score Over Number of Reviews", xlab = "Cumulative Review Count",ylab = "Average Influencer Score", pch = 20)
```

```{r}
s3d3 = scatterplot3d(score_by_friends$total_friends, score_by_friends$cummulative_influenced, score_by_friends$cummulative_influencer,
              main = "Cumulative Influenced vs Influencer Score Across Friend Count", xlab = "Cumulative Number of Friends", ylab = "Avg. Influenced Score", zlab = "Avg. Influencer Score", pch = 20, angle = 40)
fit = lm(score_by_friends$cummulative_influencer ~ score_by_friends$total_friends+ score_by_friends$cummulative_influenced)
s3d3$plane3d(fit)
```

```{r}
s3d4 = scatterplot3d(score_by_reviews$total_reviews, score_by_reviews$cummulative_influenced, score_by_reviews$cummulative_influencer,
              main = "Cumulative Influenced vs Influencer Score Across Review Count", xlab = "Cumulative Number of Friends", ylab = "Avg. Influenced Score", zlab = "Avg. Influencer Score", pch = 20, angle = 40)
fit = lm(score_by_reviews$cummulative_influencer ~ score_by_reviews$total_reviews+ score_by_reviews$cummulative_influenced)
s3d4$plane3d(fit)
```

